[Re] Spike Timing Dependent Plasticity Finds the Start of Repeating Patterns in Continuous Spike Trains

### 2018-06-19 article/Hathway-Goodman-2018.tex
Fixed random seeds: code is now deterministic. Added Fig 9 and Fig10

\begin{figure}
\centering
\includegraphics{figures/fig2_learningrules.pdf}
\caption{Effect of different learning rules on synaptic weight. We
compare the all-to-all (ATA, \textbf{A}), nearest neighbor (NN,
\textbf{B}), and reduced nearest neighbor (RNN, \textbf{C}) learning
rules for a case in which the presynaptic neuron (green dots) spikes
more often than the postsynaptic neuron (blue dots). Grey lines indicate
which spike pairs are taken into account for the calculation of the
synaptic weight change; the sign denotes a corresponding increase (+) or
decrease (-) in weight at that spike. The synaptic weight in ATA
(\textbf{A}) and NN (\textbf{B}) experience more weight changes and also
a net decrease in weight after only a few spikes. Under the RNN rule
(\textbf{C}), there are fewer changes and - in this example - no visible
net weight change.}\label{fig:stdp}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/fig4_convergence.pdf}
\caption{Weights at converged state. The weights in the converged state
look very similar in the the original study (\textbf{A)}) and the
replication implementation (\textbf{B)}). Weights from neurons not
involved in the pattern are close to 0 (black, neurons 1000-1999),
whereas weights from some neurons involved in the pattern (neurons
0-999) are close to 1 (white, maximum value). The weights of neurons
that spike at the beginning of the pattern are nearly all close to 1 and
their added postsynaptic potentials cause a spike at the beginning of
the pattern (blue rectangle).}\label{fig:conv}
\end{figure}

@@

The timing of the output neuron spikes is slightly different in the
original study and the replication. In the original study spike times of
the input and output neurons are not restricted to fixed multiples of
the timestep, so it is extremely unlikely that two neurons will spike at
the same time. In Brian, the output neuron spikes at the beginning of a
time step and will therefore happen in the same time bin as some input
neuron spikes leading to a time difference between the spikes of
\(\Delta t=0\) where the STDP rule is undefined. Brian treats these
input neuron spikes as if they happened just before the output neuron
spike (\(\Delta t<0\), due to the scheduling of events in Brian) and
will therefore increase all those weights instead of increasing some and
decreasing others. This higher number of potentiations makes it more
difficult for the system to systematically depress unimportant weights
in order to become selective to the pattern. If the learning rule is
modified so that the synaptic weight is increased as well as depressed
when input neuron and output neuron spikes happen during the same time
step (effectively causing a smaller weight increase), the pattern is
found earlier, at around 17 s or 850 spikes (for a time step of
\(10^{-4}s\)) which is close to the performance for smaller time steps
(\(10^{-6}s\)) and the original paper (both 14 s or 700 spikes). We
didn't use this modified learning rule in the rest of the paper because
it differs from the implementation used in the majority of modelling
papers.

>>>>

\begin{figure}
\centering
\includegraphics{figures/fig2_learningrules.pdf}
\caption{Effect of different learning rules on synaptic weight. We
compare the all-to-all (ATA, \textbf{A}), nearest neighbor (NN,
\textbf{B}), and reduced nearest neighbor (RNN, \textbf{C}) learning
rules for a case in which the presynaptic neuron (green dots) spikes
more often than the postsynaptic neuron (blue dots). Grey lines indicate
which spike pairs are taken into account for the calculation of the
synaptic weight change; the sign denotes a corresponding increase (+) or
decrease (-) in weight at that spike. The synaptic weight in ATA
(\textbf{A}) and NN (\textbf{B}) experience more weight changes and also
a net decrease in weight after only a few spikes. Under the RNN rule
(\textbf{C}), there are fewer changes and --- in this example --- no
visible net weight change.}\label{fig:stdp}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/fig4_convergence.pdf}
\caption{Weights at converged state. This figure shows a raster plot of
the input spikes at the end of the simulation (converged state) with the
color of the dots indicating the synaptic weight. The final weights in
the converged state look very similar in the the original study
(\textbf{A)}) and the replication implementation (\textbf{B)}). Weights
from neurons not involved in the pattern are close to 0 (black, neurons
1000-1999), whereas weights from some neurons involved in the pattern
(neurons 0-999) are close to 1 (white, maximum value). The weights of
neurons that spike at the beginning of the pattern are nearly all close
to 1 and their added postsynaptic potentials cause a spike at the
beginning of the pattern (blue rectangle).}\label{fig:conv}
\end{figure}

@@

The spike times of the output neuron are slightly different in the
original study and the replication. In the original study spike times of
the input and output neurons are not restricted to fixed multiples of
the timestep, so it is extremely unlikely that two neurons will spike at
the same time. In Brian, the output neuron spikes at the beginning of a
time step and will therefore happen in the same time bin as some input
neuron spikes leading to a time difference between the spikes of
\(\Delta t=0\) where the STDP rule is undefined. Brian treats all of the
input neuron spikes in this time bin as if they happened just before the
output neuron spike (\(\Delta t<0\), due to the scheduling of events in
Brian) and will therefore increase all those weights instead of
increasing some and decreasing others. This higher number of
potentiations makes it more difficult for the system to systematically
depress unimportant weights in order to become selective to the pattern.

If the learning rule is modified so that the change in synaptic weight
reflects that on average half the input neurons spike before the output
neuron and the other half afterwards (by adding the mean of LTP and LTD
traces), the pattern is found earlier, at around 17 s or 850 spikes (for
a time step of \(10^{-4}s\)) which is close to the performance for
smaller time steps (\(10^{-6}s\)) and the original paper (both 14 s or
700 spikes). This modified learning rule was only used to determine the
time until finding (Fig.~\ref{fig:find}) because it differs from the
implementation used in the majority of modelling papers.
